### 2017-03-20 ResearchNotes/stat_exps.tex
Adds notes about new dataset and experiment 5

\subsection{\texttt{DAT\_002} - Results and Logs}
\label{sec:dat_002}

This dataset only contains features which a number type. Each object is
calculated from the records of a single student and relates the number of
enrolled courses, number of approved courses, number of each CRUD activity and
overall number of activities. The records come from the \texttt{Results} and
\texttt{MoodleLogs} datasets. Table~\ref{tab_dat_002} shows the features of
this dataset.

@@

@@

\subsection{\texttt{EXP\_004} - clustering Number of Approved Courses Based on
Moodle Usage}

@@

>>>>

\subsection{\texttt{DAT\_002} - Number of Courses and Logs}
\label{sec:dat_002}

This dataset only contains features which a number type. Each object is
calculated from the records of a single student and relates the number of
enrolled courses, number of approved courses, number of each CRUD activity and
overall number of activities. The records come from the \texttt{Results} and
\texttt{MoodleLogs} datasets. Table~\ref{tab:dat_002} shows the features of
this dataset.

@@

\subsection{\texttt{DAT\_003} - Student/Course Profile and Results}
\label{sec:dat_003}

In this dataset we relate the profiling of a student in a courses and his
results on that course. To begin constructing this dataset we use the Profiling
dataset, as shown in section~\ref{sec:data_profiling}.

The Profiling dataset contains a results field, however, the meaning of each
value in this field is unknown. So initially, this field is dropped. To get the
actual results of student we need the Results dataset.

Each object of Profile contains the features \texttt{CourseCodeMoodle},
\texttt{CourseId}, and \texttt{StudentsId}. But the Results dataset has
\texttt{CourseCodeSiiue} and \texttt{StudentsNumber}. In order to relate both,
the Students dataset and the CoursesGeneral dataset are needed.

These datasets are related and some fields are dropped in order to produce a
dataset with the features listed in table~\ref{tab:dat_003}.

Like in dataset~\ref{sec:dat_001}, the class of this dataset may be binary, in
which the student is approved or not, or divided in groups of 2 or 4.

    \begin{tabular}{| l | l | l |}
        \hline
        \textbf{Field}               & \textbf{Source Dataset} & \textbf{Type} \\ \hline
        \texttt{CourseCodeSiiue}     & CoursesGeneral          & String        \\ \hline
        \texttt{NumberOfResources}   & Profile                 & Number        \\ \hline
        \texttt{NumberOfActivities}  & Profile                 & Number        \\ \hline
        \texttt{NumberOfViews}       & Profile                 & Number        \\ \hline
        \texttt{NumberOfSubmissions} & Profile                 & Number        \\ \hline
        \texttt{Class}               & Results                 & Binary        \\ \hline
    \end{tabular}

    \caption
        [Dataset 003]
        {Dataset 003}

    \label{tab:dat_003}
\end{table}

@@

\subsection{\texttt{EXP\_004} - Clustering Number of Approved Courses Based on
Moodle Usage}

@@

\subsection{\texttt{EXP\_005} - Predicting Students Grades From Course
Profiling}

Experiment uses \texttt{DAT\_003}, described in section~\ref{sec:dat_003}.

\begin{verbatim}
Results are similar to EXP_001, but performs worse. Meaning that looking into
Moodle usage data produces more accurate results then course profiling.
\end{verbatim}
